---
title: "Analyses from the FuturePhy Hexapod group"
author: Brian O'Meara
output: html_document
---

# State of the hexapod tree of life

This is work *in progress* from the Hexapod FuturePhy group (meeting in Chicago, Aug. 1-3, 2018). It will update as we add information.

```{r summary, echo=FALSE, message=FALSE}
library(treemap)
loadd(taxa_col)
taxa_col$OrderOnly <- gsub("Hexapoda: ","", taxa_col$Order)
```

For example, we are planning to gather info on `r length(taxa_col$Family)` families so far, but other families will be added.

The code for these analyses is all in https://github.com/bomeara/hexapods. The ROpenSci package `drake` is used to dynamically run analyses to generate content (including this page).


## Binomials per clade in GenBank

```{r plotgenbankknown, echo=FALSE, message=FALSE, fig.width=14, fig.height=14}
treemap::treemap(taxa_col, index=c("OrderOnly", "Family"), vSize="genbank.known.count", type="index")
```

## Dark taxa per clade in GenBank

```{r plotgenbankdark, echo=FALSE, message=FALSE, fig.width=14, fig.height=14}
treemap::treemap(taxa_col, index=c("OrderOnly", "Family"), vSize="genbank.dark.count", type="index")
```

## BOLD taxa per clade in GenBank

```{r plotgenbankbold, echo=FALSE, message=FALSE, fig.width=14, fig.height=14}
treemap::treemap(taxa_col, index=c("OrderOnly", "Family"), vSize="genbank.BOLD.count", type="index")
```

## Species in GenBank vs diversity in Catalog of Life

```{r plotgbvscol, echo=FALSE, message=FALSE, fig.width=14, fig.height=14}
  taxa_col_present <- subset(taxa_col, taxa_col$col.species.count>0)
  plot(x=taxa_col_present$col.species.count, y=taxa_col_present$genbank.known.count, pch=19, xlab="Number of species in Catalog of Life", ylab="Number of binomial species in GenBank", bty="n")
```

## Funding

The core grant for this was NSF [FuturePhy grant ID]. Participation and tools was also supported by grants [GN], [Phylotastic], [more]
