---
title: "Analyses from the FuturePhy Hexapod group"
author: Brian O'Meara
output: html_document
---

# State of the hexapod tree of life

This is work *in progress* from the Hexapod FuturePhy group (meeting in Chicago, Aug. 1-3, 2018). It will update as we add information.

```{r summary, echo=FALSE, message=FALSE}
library(treemap)
loadd(taxa_df)
loadd(taxa_dark)
taxa_dark$OrderOnly <- gsub("Hexapoda: ","", taxa_dark$Order)
```

For example, we are planning to gather info on `r length(taxa_df$Family)` families so far, but other families will be added.

The code for these analyses is all in https://github.com/bomeara/hexapods. The ROpenSci package `drake` is used to dynamically run analyses to generate content (including this page).


## Binomials per clade in GenBank

```{r plotgenbankknown, echo=FALSE, message=FALSE, fig.width=14, fig.height=14}
treemap::treemap(taxa_dark, index=c("OrderOnly", "Family"), vSize="genbank.known.count", type="index")
```

## Dark taxa per clade in GenBank

```{r plotgenbankdark, echo=FALSE, message=FALSE, fig.width=14, fig.height=14}
treemap::treemap(taxa_dark, index=c("OrderOnly", "Family"), vSize="genbank.dark.count", type="index")
```

## BOLD taxa per clade in GenBank

```{r plotgenbankbold, echo=FALSE, message=FALSE, fig.width=14, fig.height=14}
treemap::treemap(taxa_dark, index=c("OrderOnly", "Family"), vSize="genbank.BOLD.count", type="index")
```

## Funding

The core grant for this was NSF [FuturePhy grant ID]. Participation and tools was also supported by grants [GN], [Phylotastic], [more]
